Dominance Regions for Rank Two Cluster Algebras

### 2022-04-07 dominance_regions.tex
Lots of symbols
another way
superscripts

  Our goal in this note is to explicitly compute the possible bases which are pointed with respect to the embedding $\cA(b,c)\into\ZZ[x_k^{\pm1},x_{k+1}^{\pm1}]$ for every $k\in\ZZ$.
  That is, a basis element with \emph{$\bfg$-vector} $\lambda=(\lambda_0,\lambda_1)\in\ZZ^2$ when expanded in terms of $\{x_0,x_1\}$ can be written in the form
  \begin{equation}
    \label{eq:pointed}
    x_0^{\lambda_0}x_1^{\lambda_1}\sum\limits_{a_0,a_1 \ge 0} c^\lambda_{a_0,a_1} x_0^{-ba_0} x_1^{ca_1}
  \end{equation}
  with $c^\lambda_{0,0}=1$.
  Being \emph{pointed} means an analogous structure reproduces after expanding in terms of any pair $\{x_k,x_{k+1}\}$.
  %The collection of all $\bfg$-vectors $\lambda\in\ZZ^2$ parametrize the elements of any pointed basis.

@@

\section{Chebyshev Polynomials}
  \label{sec:chebyshev}
  Define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
  Observe that, by an easy induction, $u_{-i,\varepsilon}=-u_{i,\varepsilon}$.

>>>>

  Our goal in this note is to explicitly compute the possible bases which are pointed with respect to the embedding $\cA(b,c)\into\ZZ[x_k^{\pm1},x_{k+1}^{\pm1}]$ for every $k\in\ZZ$.
  That is, a basis element with \emph{$\bfg$-vector} $\lambda=(\lambda_0,\lambda_1)\in\ZZ^2$ when expanded in terms of $\{x_0,x_1\}$ can be written in the form
  \begin{equation}
    \label{eq:pointed}
    x_0^{\lambda_0}x_1^{\lambda_1}\sum\limits_{\alpha_0,\alpha_1 \ge 0} \rho_{\alpha_0,\alpha_1} x_0^{-b\alpha_0} x_1^{c\alpha_1}
  \end{equation}
  with $c_{0,0}=1$.
  Being \emph{pointed} means an analogous structure reproduces after expanding in terms of any pair $\{x_k,x_{k+1}\}$.
  %The collection of all $\bfg$-vectors $\lambda\in\ZZ^2$ parametrize the elements of any pointed basis.

@@

\section{Chebyshev Polynomials}
  \label{sec:chebyshev}
  Define \emph{two-parameter Chebyshev polynomials} $u_i^\varepsilon$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
  \[u_0^\varepsilon=0,\quad u_1^\varepsilon=1,\quad u_{i+1}^\varepsilon=\begin{cases} bu_i^{-\varepsilon}-u_{i-1}^\varepsilon & \text{if $\varepsilon=+$;}\\ cu_i^{-\varepsilon}-u_{i-1}^\varepsilon & \text{if $\varepsilon=-$.} \end{cases}\]
    Observe that, by an easy induction, $u_{-i}^\varepsilon=-u_i^\varepsilon$.
